---
title: "APM1110 - FA5"
author: "Betita, Jezel"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    latex_engine: xelatex
header-includes:
  - \usepackage{amssymb}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[GitHub Link](https://github.com/JezelJB/APM1110/tree/main/FAs/FA5)

**1. (Discrete Random Variables)**
**A discrete random variable X has the following probability mass function (PMF):**

$$
P(X=x)=
\begin{cases}
k(2x+1), & x=1,2,3,4\\
0, & \text{otherwise}
\end{cases}
$$

**a) Find the value of constant k.**

```{r}

x <- 1:4

k <- round(1 / sum(2*x + 1), 4)
k

```

**b) Compute the expected value E[X] and the variance Var(X).**

```{r}

pmf <- round(k * (2*x + 1), 4)
pmf

ex <- round(sum(x * pmf), 4)
ex

varx <- round(sum((x - ex)^2 * pmf), 4)
varx

```

**c) Calculate P(X >= 3).**

```{r}

sum(pmf[x >= 3])

```

**2. (Binomial Distribution)**
**An IT system detects that roughly 8% of incoming external requests are malicious. In a random sample of 20 requests:**

```{r}

n <- 20
p <- 0.08

```

**a) What is the probability that exactly 2 requests are malicious?**

```{r}

two <- round(dbinom(2, size = n, prob = p), 4)
two

```

**b) What is the probability that at least 3 requests are malicious?**

```{r}

thr <- round(1 - pbinom(2, size = n, prob = p), 4)
thr

```

**c) Determine the mean and standard deviation of the number of malicious requests.**

```{r}

n * p

sd <- round(sqrt(n * p * (1 - p)), 4)
sd

```

**3. (Poisson Distribution)**
**A server receives and average of 5.4 web traffic hits per minute. Assuming the arrival rate follows a Poisson process:**

```{r}

lambda1 <- 4.5

```

**a) Find the probability of receiving exactly 6 hits in a given minute.**

```{r}

six <- round(dpois(6, lambda1), 4)
six

```

**b) Find the probability of receiving at most 2 hits in a given minute.**

```{r}

tw <- round(1 - ppois(1, lambda1), 4)
tw

```

**c) Calculate the probability of receiving more than 10 hits in a 2-minute interval.**

```{r}

lambda2 <- 4.5 * 2

tentw <- round(1 - ppois(10, lambda2), 4)
tentw

```

**4. (Continuous Probability & Normal Distribution)**
**The processing time for a complex database query is normally distributed with a mean μ = 120 milliseconds and a standard deviation σ = 15 milliseconds.**

```{r}

mu <- 120
sigma <- 15

```

**a) What proportion of queries take longer than 135 milliseconds to process?**

```{r}

otf <- round(1 - pnorm(135, mean = mu, sd = sigma), 4)
otf

```

**b) Find the probability that a randomly chosen query takes between 100 and 130 milliseconds.**

```{r}

oot <- round(pnorm(130, mean = mu, sd = sigma) - pnorm(100, mean = mu, sd = sigma), 4)
oot

```

**c) Find the 95th percentile of query processing times.**

```{r}

perc <- round(qnorm(0.95, mean = mu, sd = sigma), 4)
perc

```
