---
title: "APM1110 - FA4"
author: "Betita, Jezel"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[GitHub Link](https://github.com/JezelJB/APM1110/tree/main/FAs/FA4)

**2.  A binary communication channel carries data as one of two sets of signals denoted by 0 and 1. Owing to noise, a transmitted 0 is sometimes received as a 1, and a transmitted 1 is sometimes received as a 0. For a given channel, it can be assumed that a transmitted 0 is correctly received with probability 0.95, and a transmitted 1 is correctly received with probability 0.75. Also, 70% of all messages are transmitted as a 0. If a signal is sent, determine the probability that:**

**(a) a 1 was received;**

```{r}
r0t0 <- 0.95
r1t0 <- 1 - r0t0

r1t1 <- 0.75

t0 <- 0.70
t1 <- 1 - t0

pr1 <- (t1 * r1t1) + (t0 * r1t0)
pr1
```

**(b) a 1 was transmitted given than a 1 was received.**

```{r}
ptr1 <- (t1 * r1t1) / pr1
ptr1
```

**7.  There are three employees working at an IT company: Jane, Amy, and Ava, doing 10%, 30%, and 60% of the programming, respectively. 8% of Jane’s work, 5% of Amy’s work, and just 1% of Ava‘s work is in error. What is the overall percentage of error? If a program is found with an error, who is the most likely person to have written it?**

```{r}
library(formattable)

# Jane's Work & Error
j <- 0.10
ej <- 0.08

# Amy's Work & Error
am <- 0.30
eam <- 0.05

# Ava's Work & Error
av <- 0.60
eav <- 0.01

# Overall Percentage of Error

pe <- (j * ej) + (am * eam) + (av * eav)
percent(pe)

# Program with an Error written by:

# Jane
pje <- (j * ej) / pe

# Amy
pame <- (am * eam) / pe

# Ava
pave <- (av * eav) / pe

prog_er <- c(pje, pame, pave)
work_er <- max(prog_er)
percent(work_er)
```

**A program error was most likely written by Amy.**
