---
title: "APM1110 - FA6"
author: "Betita, Jezel"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**I. Geometric Distribution**

Provide an R code for the geometric disrtibution. The geometric distribution is a probability distribution that models the number of trials required to achieve the first success in a sequence of Bernoulli trials, where each trial has a constant probability of success.

**1. Set the probability to p <- 0.2**

```{r}

p <- 0.2

```

**2. Generate 1000 random variables from the geometric distribution.**

```{r}

x <- rgeom(1000, prob = p) + 1

```

**3. Calculate basic statistics:**

```{r}

mean_x <- mean(x)
var_x <- var(x)
sd_x <- sd(x)

```

**4. Print the results in item 3 with the following output format:**

```{r}

cat("Number of trials required to achieve first success:", x[1], "\n")
cat("Mean:", round(mean_x, 2), "\n")
cat("Variance:", round(var_x, 2), "\n")
cat("Standard deviation:", round(sd_x, 2), "\n")

```

**5. Plot the histogram of the results.**

```{r}

hist(x,
     main = "Geometric Distribution",
     xlab = "Number of Trials (until first success)",
     ylab = "Frequency",
     col = "lightpink")

cat("Number of trials required to achieve first success:", x[1], "\n")

```



**II. Hypergeometric Distribution**

Consider a plant manufacturing IC chips which 10% are expected to be defective. The chips are packed in boxes for export. Before transportation, a sample is drawn from each box. Estimate the probability that the sample contains more than 10% defectives, when:

**1. A sample of 10 is selected from a box of 40;**

```{r}

samp <- 10

total1 <- 40
defec1 <- 4

num1 <- 1 - phyper(1, defec1, total1 - defec1, samp)

cat("Probability that sample contains more than 10% defectives (from a box of 40):",
    round(num1, 2), "\n")

```

The possibility of the sample that includes more than 10% defected chips is 0.26. Which means, there is a 26% chance that more than 1 chip is defective among the 10 chips selected.


**2. A sample of 10 is selected from a box of 5000.**

```{r}

total2 <- 5000
defec2 <- 500

num2 <- 1 - phyper(1, defec2, total2 - defec2, samp)

cat("Probability that sample contains more than 10% defectives (from a box of 5000):",
    round(num2, 2), "\n")

```

The probability is 0.26. There is a 26% chance that more than 1 chip is defective among the 10 chips selected.


The probabilities of the two boxes are similar because both contains 10% defective rate.
